---
title: "2019 Playoffs?!? League Champion's Address"
author: "Jerry's Belt Buckle\n(Chris Umphlett)"
date: "(updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

library(tidyverse)
```

   
---

``` {r create_loop_parms, echo = FALSE}

teams <- c("Jerry's Belt Buckle",
           "The Institute",
           "Kayak Pirates",
           "The Maccabee",
           "The Commish",
           "K Rabbits",
           "Black is for Sunday",
           "The Icon",
           "40 Acres and a Mule",
           "Show Me Da Money!"
           )

record <- c("12 - 2 (1st)",
            "12 - 2 (2nd)",
            "10 - 4 (3rd)",
            "7 - 7 (4th)",
            "5 - 9 (5th)",
            "5 - 9 (6th)",
            "6 - 8 (7th)",
            "6 - 8 (8th)",
            "4 - 10 (9th)",
            "3 - 11 (10th)"
            )

finish <- c("Champion",
            "First Loser",
            "3rd",
            "4th",
            "5th",
            "6th",
            "7th",
            "8th",
            "Did not qualify",
            "Did not qualify"
            )

```

---

<iframe width="560" height="315" src="https://www.youtube.com/embed/yR_2GQ6mZLc?start=42" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

``` {r yahoo_api}
#http://ryankuhn.net/blog/Fantasy-Football-in-R-Part-I
# Setup the environment
# library(httr)
# library(XML)
# library(httpuv)
# options("httr_oob_default" = T)

# Setup the app
# yahoo_key <- invisible(Sys.getenv("yahoo_key"))
# yahoo_secret <- invisible(Sys.getenv("yahoo_secret"))
# 
# yahoo <- oauth_endpoints("yahoo")
# 
# myapp <- oauth_app("yahoo", key = yahoo_key, secret = yahoo_secret)
# yahoo_token <- oauth2.0_token(yahoo, myapp, cache = T, use_oob = T)
# sig <- sign_oauth1.0(myapp, yahoo_token$oauth_token, yahoo_token$oauth_token_secret)
```

``` {r loop_function, results = "asis"}
i <- 1

xarin_fun <- function() {

  for (team in teams) {

    cat("---")
    cat(paste0("\n # ", team, "\n\n"))
    cat(paste0("Regular season record: ", record[i], "\n\n"))
    cat(paste0("Playoff finish: ", finish[i], "\n\n"))
    i <- i + 1
  }
}

# xarin_fun()
```

---

## Awards
### Heart and Soul of Jerry's Belt Buckle

<iframe width="560" height="315" src="https://www.youtube.com/embed/oqafyEW5PPA?start=38&end=55" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

## Awards
### Keeper of the year

Some of you scoffed when I selected him with the 16th round draft pick in 2017. One of you acquired Le'Veon Bell and would not offer much of anything in a trade for him. All of you wished you had him. The foundation of my dominant season started with this guy.
 
<iframe width="560" height="315" src="https://www.youtube.com/embed/n6y06uCUEvo?start=0&end=20" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

## Awards
### Rookie of the year

<iframe width="560" height="315" src="https://www.youtube.com/embed/CEMzXOpVkzI" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

<iframe width="560" height="315" src="https://www.youtube.com/embed/SFEW9o0nauc" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

## Awards
### Solution to a problem I could never solve guy

Over the years I've had a hate-hate relationship with the TE position. Last year I finally decided to reach a bit to get some security. 

Kelce
<iframe width="560" height="315" src="https://www.youtube.com/embed/OCLQ8mNYlgE?start=86&end=104" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

## Awards
### Mid-season acquisition of the year

I traded for this guy to raise the ceiling of my team. It paid off when __
Watson
<iframe width="560" height="315" src="https://www.youtube.com/embed/u34s4UTplLM?start=225&end=237" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---
<iframe width="560" height="315" src="https://www.youtube.com/embed/2nPSP_N6NLs" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
